Early Observations of \abc:\\ \textbf{a Type Ia Supernova Featuring Either} Strong Ejecta Mixing and/or Interaction with Diffuse Material

### 2017-10-30 doc/ms.tex
add text to describe velocity evolution relative to Branch SNe sample

Using the SuperNova IDentification (\texttt{SNID}; \citealt{2007ApJ...666.1024B}) package, 
we find the low-resolution spectrum of \abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic features of a SN
Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified in the spectra of \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \, \mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of the absorption features near 5750 and 6100 \AA, which are respectively attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\ and $-55 \pm 5$\,\AA, respectively. According to the classification scheme presented in \citet{2009PASP..121..238B}, these pEW measurements indicate that \abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes.

>>>>

Using the SuperNova IDentification (\texttt{SNID};
\citealt{2007ApJ...666.1024B}) package, we find the low-resolution spectrum of
\abc\ at $+18.8$\,d is best matched by normal SNe Ia. Several characteristic
features of a SN Ia, such as \ion{Si}{2}, \ion{S}{2}, can be easily identified
in the spectra of \abc\ (Figure \ref{fig:spec_seq}). From the $+3.7 \,
\mathrm{d}$ LCO spectrum, we measure the pseudo-equivalent widths (pEWs) of
the absorption features near 5750 and 6100 \AA, which are respectively
attributed to \ion{Si}{2}\,$\lambda\lambda$6580, 7234, to be $-12 \pm 2$\,\AA\
and $-55 \pm 5$\,\AA, respectively. According to the classification scheme
presented in \citet{2006PASP..118..560B}, these pEW measurements indicate that
\abc\ is a shallow silicon SN, similar to the SN\,1999aa-likes
\citep{2009PASP..121..238B}. \textbf{In Figure~\ref{fig:branch_vel}, the
velocity evolution of \ion{Si}{2}$\,\lambda6355$ in \abc\ is compared to the
median evolution of the four spectroscopic subclasses defined in
\citet{2006PASP..118..560B}. The median evolution is defined using the sample
of SNe Ia in \citet{2012AJ....143..126B}. For each SN, we interpolate the
\ion{Si}{2} velocity, $v_{\ion{Si}{2}\,\lambda6355}$, to a fixed grid at 1\,d
intervals. We then take the median $v_{\ion{Si}{2}\,\lambda6355}$ for each
point on the grid, and only retain those points with at least 3 SNe (to
prevent the early and late evolution to be defined by a single SN). The
evolution of \ion{Si}{2} is most reminicent of the shallow-silicon subclass
defined in \citet{2006PASP..118..560B}.}

\begin{figure}[htb]
  \centering
  \includegraphics[width=0.48\textwidth]{Branch_vel_evol.pdf}
  \caption{\textbf{Velocity evolution of \ion{Si}{2},   
           $v_{\ion{Si}{2}\,\lambda6355}$, for \abc\ compared to the median 
           evolution of the four spectroscopic subclasses defined in 
           \citet{2006PASP..118..560B}, using data from 
           \citet{2012AJ....143..126B}. Typical uncertainties for \abc\ are 
           $\sim$1000\,km\,s$^{-1}$ before $T_{B,\mathrm{max}}$, when the 
           \ion{Si}{2}$\,\lambda6355}$ profile is shallow and the minimum of 
           absorption is difficult to determine, and $\sim$300\,km\,s$^{-1}$ 
           after $T_{B,\mathrm{max}}$. For the median curves, the typical 
           scatter, determined via the interquartile range of the sample, is 
           XXX $\sim$200\,km\,s$^{-1}$ XXX, around $T_{B,\mathrm{max}}$.
           At early times, core-normal and broad-line SNe have significantly 
           faster \ion{Si}{2} than \abc, while the declining trend of cool SNe 
           does not match \abc.}
  }
  \label{fig:branch_vel}
\end{figure}
